---
title: "TidyModel Practice"
author:
  - name: Thomas Reinke
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    toc: yes
    toc_depth: 4
    df_print: kable
editor_options:
  chunk_output_type: console
  # html_document:
  #   theme: sandstone
  #   highlight: tango
  #   toc: true
  #   numbered_sections: true
  #   toc_float: true
  #   toc_depth: 4
  #   df_print: kable
  #   df_print: paged
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(broom.mixed)
library(dotwhisker)
library(rstanarm)
library(knitr)
knitr::opts_chunk$set(echo = TRUE, class.output="bg-warning")
```

# Intro to Tidymodels

## Frequentist

### Sea Urchin Data

```{r}
#| message: false

url <- "https://tidymodels.org/start/models/urchins.csv"
urchins <-
  read_csv(url) %>% 
  # Change the names to be a little more verbose
  setNames(c("food_regime", "initial_volume", "width")) %>% 
  # Factors are very helpful for modeling
  # so we convert one column
  mutate(
    food_regime = factor(
      food_regime,
      levels = c("Initial", "Low", "High")
    )
  )
```

### Scatterplot by Regime

```{r}
#| message: false
ggplot(urchins,
       aes(x = initial_volume, 
           y = width, 
           group = food_regime, 
           col = food_regime)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) +
  scale_color_viridis_d(option = "plasma", end = .7)
```

### Build and Fit a Model

```{r}
#| message: false
# linear_reg() |> 
#   set_engine("keras")
lm_mod <- linear_reg()

lm_fit <- 
  lm_mod %>% 
  fit(width ~ initial_volume * food_regime, data = urchins)
#lm_fit
```

### View Fit

```{r}
tidy(lm_fit)
```

### Dot & Whisker Plot

```{r}
tidy(lm_fit) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```

### Prediction

#### Prediction Points

```{r}
new_points <- expand.grid(initial_volume = 20, 
                          food_regime = c("Initial", "Low", "High"))
new_points
```

#### Mean Prediction

```{r}
mean_pred <- predict(lm_fit, new_data = new_points)
mean_pred
```

#### Confidence Interval

```{r}
conf_int_pred <- predict(lm_fit, 
                         new_data = new_points, 
                         type = "conf_int")
conf_int_pred
```

#### Plot Intervals

```{r}
# Now combine: 
plot_data <- 
  new_points %>% 
  bind_cols(mean_pred) %>% 
  bind_cols(conf_int_pred)

# and plot:
ggplot(plot_data, aes(x = food_regime)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower, 
                    ymax = .pred_upper),
                width = .2) + 
  labs(y = "urchin size")
```

## Bayes

### Build Model

```{r}
#| cache: true
# set the prior distribution
options(mc.cores = parallel::detectCores())
prior_dist <- rstanarm::student_t(df = 1)

set.seed(123)

# make the parsnip model
bayes_mod <-   
  linear_reg() %>% 
  set_engine("stan", 
             prior_intercept = prior_dist, 
             prior = prior_dist) 

# train the model
bayes_fit <- 
  bayes_mod %>% 
  fit(width ~ initial_volume * food_regime, data = urchins)

print(bayes_fit, digits = 5)
```

### Confidence Intervals

```{r}
tidy(bayes_fit, conf.int = TRUE)
```

### Plot Error Bars

```{r}
bayes_plot_data <- 
  new_points %>% 
  bind_cols(predict(bayes_fit, new_data = new_points)) %>% 
  bind_cols(predict(bayes_fit, new_data = new_points, type = "conf_int"))

ggplot(bayes_plot_data, aes(x = food_regime)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower, ymax = .pred_upper), width = .2) + 
  labs(y = "urchin size") + 
  ggtitle("Bayesian model with t(1) prior distribution")
```

# Preprocessing

## Introduction

```{r}
library(nycflights13)
library(skimr)
library(timeDate)
```

## The New York City Flight Data

Goal: predict whether or not a plane arrives 30+ minutes late.

```{r}
set.seed(123)

flight_data <-
  flights |>
  mutate(
    arr_delay = ifelse(arr_delay >= 30, "late", "on_time"),
    arr_delay = factor(arr_delay),
    date = as_date(time_hour)
  ) |>
  inner_join(weather, by = c("origin", "time_hour")) |>
  select(dep_time, flight, origin, dest, air_time,
         distance, carrier, date, arr_delay, time_hour) |>
  na.omit() |>
  mutate_if(is.character, as.factor)
```

```{r}
flight_data |> 
  count(arr_delay) |>
  mutate(prop = n/sum(n))
```

```{r}
#| eval: false
glimpse(flight_data)
```

```{r}
flight_data |> skim(dest, carrier)
```

## Data Splitting

```{r}
set.seed(222)

data_split <- initial_split(flight_data, prop = 3/4)

train_data <- training(data_split)
test_data <- testing(data_split)
```

## Create Recipe and Roles

```{r}
flights_rec <-
  recipe(arr_delay ~ ., data = train_data) |>
  update_role(flight, time_hour, new_role = "ID")
```

```{r}
#| eval: false
summary(flights_rec)
```

## Create Features

```{r}
#| eval: false
flight_data |>
  distinct(date) |> 
  mutate(numeric_date = as.numeric(date))
```

```{r}
flights_rec <-
  flights_rec |> 
  step_date(date, features = c("dow", "month")) |>
  step_holiday(date,
               holidays = listHolidays("US"),
               keep_original_cols = FALSE) |>
  step_dummy(all_nominal_predictors())
```

```{r}
test_data |>
  distinct(dest) |>
  anti_join(train_data)
```

```{r}
flights_rec <-
  flights_rec |>
  step_zv(all_predictors())
```

## Fit a Model with a Recipe

```{r}
lr_mod <-
  logistic_reg() |>
  set_engine("glm")
```

1. Process recipe using training set
2. Apply recipe to training set
3. Apply recipe to test set

```{r}
flights_wflow <-
  workflow() |>
  add_model(lr_mod) |>
  add_recipe(flights_rec)

flights_wflow
```

```{r}
flights_fit <-
  flights_wflow |>
  fit(data = train_data)
```

```{r}
#| cache: true
flights_fit |>
  extract_fit_parsnip() |>
  tidy()
```

## Use a Trained Workflow to Predict

```{r}
#| eval: false
predict(flights_fit, test_data)
```

```{r}
flights_aug <-
  augment(flights_fit, test_data)
```

```{r}
#| eval: false
flights_aug |>
  select(arr_delay, time_hour, flight, .pred_class, .pred_on_time)
```

```{r}
flights_aug |>
  roc_curve(truth = arr_delay, .pred_late) |>
  autoplot()
```

```{r}
flights_aug |>
  roc_auc(truth = arr_delay, .pred_late)
```